SunPy - Python for Solar Physics

### 2014-08-27 2-Data_Types.tex

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} has this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.

>>>>

These classes allow access to the data
and associated metadata and provide appropriate convenience functions to
enable analysis and visualisation. For each of these classes, the data is
stored in the \texttt{data} attribute, while the metadata should be stored 
in the \texttt{meta} attribute (currently, only \texttt{Map} and \texttt{LightCurve} have this feature 
fully implemented). 
% schriste - change this until all fixed
It is possible to instantiate the
data types from various
different sources: e.g., files, URLs, and arrays.  
In order to provide instrument-specific specialisation, the core SunPy classes 
make use of subclassing; e.g., \texttt{Map} has an \texttt{AIAMap} 
sub-type for data from the \textit{SDO}/AIA instrument.
